Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-24 sattose/paper.tex
Table makeup

\begin{table}[H]
\begin{tabular}{|l|l|}
\hline
Amount of projects                                                                                      & 3.848      \\ \hline
Amount of lines                                                                                         & 8.284.140  \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\ whitespace, comments, etc.)\end{tabular}        & 8.163.429  \\ \hline
Amount of statements/declarations                                                                       & 6.863.725  \\ \hline
Amount of tokens                                                                                        & 66.964.270 \\ \hline
Amount of lines cloned                                                                                  & 1.341.094  \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of lines cloned (excluding\\ whitespace, comments, etc.)\end{tabular} & 815.799    \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of statements/declarations\\ cloned\end{tabular}                      & 747.993    \\ \hline
Amount of tokens cloned                                                                                 & 9.800.819  \\ \hline
Amount of clone classes                                                                                 & 34.367     \\ \hline
\end{tabular}
\end{table}

@@

\subsubsection{Our measurements}
We have recreated the same table as Fontana et al \cite{fontana2015duplicated}, but with the following differences:
\begin{itemize}
  \item We consider clone classes rather than clone pairs
\item We use different thresholds regarding when a clone should be considered.
\item We seek by statement/declaration rather than SLOC.
\item We test a broader range of projects (they use a set of 50 relatively large projects, we use a large corpus that was assembled by a machine learning algorithm testing java projects on GitHub for quality, which contains projects of all sizes and with differing code quality)
\end{itemize}

@@

\begin{table}[H]
\begin{tabular}{|l|l|l|} \hline
\textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\ \hline
Unrelated          & 13.537           & 39,39               \\ \hline
Same Class          & 8.341            & 24,27               \\ \hline
Sibling            & 5.978            & 17,39               \\ \hline
Same Method         & 2.456            & 7,15                \\ \hline
External Superclass & 2.402            & 6,99                \\ \hline
First Cousin        & 695             & 2,02                \\ \hline
Superclass         & 488             & 1,42                \\ \hline
Common Hierarchy    & 442             & 1,29                \\ \hline
Ancestor           & 28              & 0,08               \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[H]
\begin{tabular}{|l|l|l|}
\hline
\textbf{Location} & \textbf{Amount} & \textbf{Percentage} \\ \hline
Method Level       & 19.817           & 57,66               \\ \hline
Class Level        & 14.366           & 41,80               \\ \hline
Interface Level    & 110             & 0,32                \\ \hline
Enum Level         & 74              & 0,22                \\ \hline
\end{tabular}
\end{table}

@@

\subsection{Clone instance contents}
Finally, we looked at the contents of individual clone instances: what kind of declarations and statements do they span. We selected the following categories to be relevant for refactoring:
\begin{enumerate}
  \item
\end{enumerate}

\begin{table}[H]
\begin{tabular}{|l|l|l|}
\hline
\textbf{Contents}       & \textbf{Amount} & \textbf{Percentage} \\ \hline
HASINTERFACEDECLARATION & 10              & 0,03                \\ \hline
SEVERALMETHODS          & 9.077            & 26,41               \\ \hline
FULLCLASS               & 198             & 0,58                \\ \hline
FULLENUM                & 4               & 0,01                \\ \hline
FULLMETHOD              & 554             & 1,61                \\ \hline
INCLUDESFIELDS          & 1.150            & 3,35                \\ \hline
HASCLASSDECLARATION     & 445             & 1,29                \\ \hline
HASENUMDECLARATION      & 47              & 0,14                \\ \hline
FULLINTERFACE           & 6               & 0,02                \\ \hline
HASENUMFIELDS           & 52              & 0,15                \\ \hline
PARTIALMETHOD           & 19.263           & 56,05               \\ \hline
ONLYFIELDS              & 565             & 1,64                \\ \hline
OTHER                   & 2.996            & 8,72                \\ \hline
\end{tabular}
\end{table}
%TODO: Finish text and add measurements.

@@

\subsubsection{Tables}

All tables must be centered, neat, clean and legible. Do not use pencil
or hand-drawn tables. Table number and title always appear before the
table.

One line space before the table title, one line space after the table
title and one line space after the table. The table title must be
initial caps and each table numbered consecutively.

\begin{table}[ht]
\begin{center}
\caption{Sample Table}

\bigskip

\begin{tabular}{|l|l|r|}
\hline
A & B & 1\\ \hline
C & D & 2\\
E & F & 3\\ \hline
\end{tabular}
\end{center}
\end{table}

\subsubsection{Handling References}

Use a first level heading for the references. References follow the
acknowledgements.

>>>>

\begin{table}[H]
  \begin{center}
  \caption{CloneRefactor results for Java projects corpus \cite{githubCorpus2013}.}
  \bigskip
\begin{tabular}{|l|l|}
\hline
Amount of projects                                                                                      & 3.848      \\ \hline
Amount of lines                                                                                         & 8.284.140  \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\ whitespace, comments, etc.)\end{tabular}        & 8.163.429  \\ \hline
Amount of statements/declarations                                                                       & 6.863.725  \\ \hline
Amount of tokens                                                                                        & 66.964.270 \\ \hline
Amount of lines cloned                                                                                  & 1.341.094  \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of lines cloned (excluding\\ whitespace, comments, etc.)\end{tabular} & 815.799    \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of statements/declarations\\ cloned\end{tabular}                      & 747.993    \\ \hline
Amount of tokens cloned                                                                                 & 9.800.819  \\ \hline
Amount of clone classes                                                                                 & 34.367     \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

\subsubsection{Our measurements}
We have recreated the same table as Fontana et al \cite{fontana2015duplicated}, but with the following differences:
\begin{itemize}
  \item We consider clone classes rather than clone pairs.
\item We use different thresholds regarding when a clone should be considered.
\item We seek by statement/declaration rather than SLOC.
\item We test a broader range of projects (they use a set of 50 relatively large projects, we use a large corpus that was assembled by a machine learning algorithm testing java projects on GitHub for quality, which contains projects of all sizes and with differing code quality).
\end{itemize}

@@

\begin{table}[H]
  \begin{center}
  \caption{Clone relations}
  \bigskip
\begin{tabular}{|l|l|l|} \hline
\textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\ \hline
Unrelated          & 13.537           & 39,39               \\ \hline
Same Class          & 8.341            & 24,27               \\ \hline
Sibling            & 5.978            & 17,39               \\ \hline
Same Method         & 2.456            & 7,15                \\ \hline
External Superclass & 2.402            & 6,99                \\ \hline
First Cousin        & 695             & 2,02                \\ \hline
Superclass         & 488             & 1,42                \\ \hline
Common Hierarchy    & 442             & 1,29                \\ \hline
Ancestor           & 28              & 0,08               \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{table}[H]
  \begin{center}
  \caption{Clone instance locations}
  \bigskip
\begin{tabular}{|l|l|l|}
\hline
\textbf{Location} & \textbf{Amount} & \textbf{Percentage} \\ \hline
Method Level       & 19.817           & 57,66               \\ \hline
Class Level        & 14.366           & 41,80               \\ \hline
Interface Level    & 110             & 0,32                \\ \hline
Enum Level         & 74              & 0,22                \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

\subsection{Clone instance contents}
Finally, we looked at the contents of individual clone instances: what kind of declarations and statements do they span. We selected the following categories to be relevant for refactoring:
\begin{enumerate}
\end{enumerate}

\begin{table}[H]
  \begin{center}
  \caption{Clone instance contents}
  \bigskip
\begin{tabular}{|l|l|l|}
\hline
\textbf{Contents}       & \textbf{Amount} & \textbf{Percentage} \\ \hline
HASINTERFACEDECLARATION & 10              & 0,03                \\ \hline
SEVERALMETHODS          & 9.077            & 26,41               \\ \hline
FULLCLASS               & 198             & 0,58                \\ \hline
FULLENUM                & 4               & 0,01                \\ \hline
FULLMETHOD              & 554             & 1,61                \\ \hline
INCLUDESFIELDS          & 1.150            & 3,35                \\ \hline
HASCLASSDECLARATION     & 445             & 1,29                \\ \hline
HASENUMDECLARATION      & 47              & 0,14                \\ \hline
FULLINTERFACE           & 6               & 0,02                \\ \hline
HASENUMFIELDS           & 52              & 0,15                \\ \hline
PARTIALMETHOD           & 19.263           & 56,05               \\ \hline
ONLYFIELDS              & 565             & 1,64                \\ \hline
OTHER                   & 2.996            & 8,72                \\ \hline
\end{tabular}
\end{center}
\end{table}
%TODO: Finish text and add measurements.

@@
